Solent region: Test Maps

### 2021-07-21 Solent_Mapping_v2.Rmd
Changing the year for the fuel poverty to 2019 to reflect what the data is

```{r Mapping the local authority energy consumption (Personal)}
# re-use the merged dataset
ggplot2::ggplot(la_merged_Transp) +
  geom_sf(aes(fill = Personal)) +
  scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
```

@@

>>>>

```{r Mapping the local authority energy consumption (Personal)}
# re-use the merged dataset
ggplot2::ggplot(la_merged_Transp) +
  geom_sf(aes(fill = Personal)) +
  scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
```
## Mapping Fuel Poverty 
### 2019 Proportion of Population

```{r Loading in the 2019 Local Authority Fuel Poverty Data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
la_fuelpov_2019<-readr::read_csv(inFile)
head(la_fuelpov_2019)
```
```{r Mapping Local Authority Fuel Poverty 2021}
la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Codes` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov2019) +
  geom_sf(aes(fill = pcFP)) +
  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
```

### Actual Difference between 2012-2019
```{r Loading in the difference data}
#Green indicates a smaller increase in fuel poverty from 2012 to 2019
#Red indicates an increase in fuel poverty from 2012 to 2019
```

###Difference in proportion between 2012-2019

@@

### Mapping Fuel Poverty
#### 2019 Fuel Poverty
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2021 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2021<-readr::read_csv (inFile)
head(lsoa_fuelpov_2021)
```

```{r Mapping the LSOA 2021 Fuel Poverty}
lsoa_fuelpov_2021$LSOA11CD <- lsoa_fuelpov_2021$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2021_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2021) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2021_merged$pcFP <- as.numeric(lsoa_fuelpov_2021_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2021_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
